---
title: "LM with Prediction"
author: "Lucille McEwen"
date: "11/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
```
  
We are using a linear model to predict a simulated strength score based on arm strength and or grip strength.  
  
```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```

## Model1  
  
  
Scatterplot SIMS as a function of ARM  

```{r}
plot(SIMS~ARM,data=dataF)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
```

##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```
```{r}
model.1=lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
new=data.frame(ARM=88,GRIP=94)
predict(model.1,new,interval="prediction")
```
This is a linear model of SIMS based on ARM strength. The adjusted R-squared is 0.467.  

## Model2

Scatterplot SIMS as a function of GRIP  

```{r}
plot(SIMS~GRIP,data=dataF)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```

##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```
```{r}
model.2=lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
predict(model.2,new,interval="prediction")
```

This is a linear model of SIMS based on GRIP strength. The adjusted R-squared is 0.4094 which is less than the one for ARM strength, so the linear model based on GRIP is better than the one based on ARM.  

## Model3  

SIMS as a function of ARM and GRIP

```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=dataF)
summary.lm(model.3)
predict(model.3,new,interval="prediction")
``` 

The adjusted R-squared for model3 is 0.5358, which is bigger than the one for GRIP. This means model 3 is better than the previous model for predicting SIMS.  
  
```{r}
anova(model.1,model.3)
```

The p-value is 0.000004994 which is less than 0.05 so we reject the null hypothesis and conclude that model 3 is better than model 1. 